Thesis Title

### 2022-03-03 chapters/introduction.tex
add phred error table

In FASTQ both the sequence letter and quality score are each encoded with a single ASCII character for brevity. The quality of a sequence in a FASTQ file is represented by a quality value Q is an integer mapping of p, where p is the probability that the corresponding base call is incorrect (see \ref{tab:PHRED_quality}). This is called the PHRED score \citep{ewing_base-calling_1998} and is defined by the following equation:

@@

%TABLE HERE - PHRED and error rate

>>>>

In FASTQ both the sequence letter and quality score are each encoded with a single ASCII character for brevity. The quality of a sequence in a FASTQ file is represented by a quality value Q is an integer mapping of p, where p is the probability that the corresponding base call is incorrect (see Table \ref{tab:phred_error}). This is called the PHRED score \citep{ewing_base-calling_1998} and is defined by the following equation:

@@

\begin{table}[h!]
\caption{\textbf{PHRED quality scores are logarithmically linked to error probabilities.} A PHRED Score of 20 indicates the likelihood of finding 1 incorrect base call among 100 bases. In other words, the precision of the base call is 99\%. $\mathbf{Q}$ scores are classified as a property that is associated logarithmically with the probabilities of base calling error $\mathbf{P}$.} \label{tab:phred_error}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Phred Quality Score} & \textbf{Probability of incorrect base call} & \textbf{Base call accuracy} \\ \midrule
10 & 1 in 10        & 90\%     \\
20 & 1 in 100       & 99\%     \\
30 & 1 in 1000      & 99.90\%  \\
40 & 1 in 10,000    & 99.99\%  \\
50 & 1 in 100,000   & 100.00\% \\
60 & 1 in 1,000,000 & 100.00\% \\ \bottomrule
\end{tabular}
\end{table}
